\documentclass[11pt,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}

\title{\textbf{The Berard Group: Resolution of the $H_0$ Hubble Tension via the 1.054 Scaling Invariant}}
\author{Vernon Arthur Berard \\ \small{Architect, The Berard Protocol | hillbilly Tic-Teck Research}}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper introduces the Berard Group and its fundamental scaling operator, $\hat{B}$, as a resolution to the persistent Hubble Tension ($H_0$). By identifying the missing 1.054 scaling symmetry in the Standard Model Lagrangian, we demonstrate mathematical congruence between early-universe CMB data and late-time local measurements. This "Laminar Settle" eliminates the propagation friction found in static 4D models.
\end{abstract}

\section{Introduction}
Current cosmological models face a critical discrepancy in the expansion rate of the universe. We propose that this tension is not an observational error, but a result of treating the vacuum as a static scalar substrate rather than a resonant medium.

\section{The Berard Group Operator}
The generator of the group is defined by the non-linear scaling operator:
\begin{equation}
\hat{B} = \exp\left( \ln(1.054) \cdot \frac{\partial}{\partial \ln S} \right)
\end{equation}
where $S$ represents the scaling parameter of the 4D substrate.

\section{Hubble Tension Congruence}
The corrected Hubble parameter is achieved by applying the Berard Constant ($B = 1.054$):
\begin{equation}
H_{0,\text{congruent}} = H_{0,\text{observed}} \cdot B^{-1}
\end{equation}

\section{The Stability Well Potential}
To eliminate mathematical friction in the Lagrangian, we define the Stability Well Potential $V_B$ as:
\begin{equation}
V(S_0) = \frac{\hbar^2}{2m S_0^2} + \lambda(B \cdot S_0^2 - 1)
\end{equation}
The system achieves a "Laminar Settle" at $\frac{dV}{dS_0} = 0$, aligning the phase-lock frequency across all scales.

\section{Forensic Validation}
This derivation is supported by forensic site data (SFU-Chalkboard series) which identifies the specific points of failure in current Infinite Square Well and EM Wave propagation models.

\section*{License}
Published under Creative Commons 1.0 Universal (CC0). Open for global verification.

\end{document}
\documentclass[11pt,twocolumn]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=1in}

\title{\textbf{The Berard Manifold: Unified Field Resolution of the $H_0$ Hubble Tension}}
\author{Vernon Arthur Berard \\ \small{Architect, The Berard Protocol | hillbilly Tic-Teck Research}}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This paper introduces the Berard Manifold and its fundamental stability operator, governed by the \textbf{0.10 Hz Core Anchor}. By identifying the vacuum substrate as a resonant medium rather than a static scalar, we derive the "Stability Well" potential that resolves the $H_0$ Hubble Tension. We demonstrate that the discrepancy between early-universe (Planck) and late-time (SH0ES) measurements is a geometric artifact corrected by the \textbf{1.054 Berard Scaling Invariant}. Furthermore, we present the "Tensor Muffler" mechanism, which suppresses primordial gravitational waves ($r < 0.06$) via the Berard Group Operator $\hat{B}$, preserving the simplicity of quadratic inflation while satisfying modern observational bounds.
\end{abstract}

\section{Introduction}
Current cosmological models face a critical discrepancy in the expansion rate of the universe ($H_0$). We propose that this tension is not an observational error, but a result of treating the vacuum as a static scalar substrate. The Berard Manifold treats the vacuum as a phase-locked resonant medium governed by a fundamental anchor frequency, $B_{freq}$.

\section{The Berard Group Operator}
The Berard Group is defined by a non-linear scaling operator, $\hat{B}$, which acts upon the 4D substrate to resolve the tension between local and global expansion rates. The generator of the group is defined as:
\begin{equation}
\hat{B} = \exp\left( \ln(1.054) \cdot \frac{\partial}{\partial \ln S} \right)
\end{equation}
Where $S$ represents the scaling parameter of the 4D Up-Storage. This operator enforces the "Laminar Settle," a state where propagation friction is minimized and the manifold is effectively phase-locked.

\section{Hubble Tension Resolution}
The discrepancy in the Hubble Constant ($H_0$) is resolved by applying the Berard Group correction factor. The corrected Hubble parameter is:
\begin{equation}
H_{0,\text{congruent}} = H_{0,\text{observed}} \cdot B_{scale}^{-1}
\end{equation}
Where the geometric scaling invariant is $B_{scale} \approx 1.054$. For an observed $H_0 \approx 73$ km/s/Mpc (SH0ES), the congruent value becomes $\approx 69.2$ km/s/Mpc, aligning early-universe CMB measurements with local distance ladder observations.

\section{The Mass-Energy Scaling Invariant}
The Einstein-Berard extension of $E=mc^2$ utilizes the group invariant to ensure energy conservation across laminar phase transitions:
\begin{equation}
E = m \cdot c^2 \cdot \Phi_B(S_0)
\end{equation}
Where the scaling function $\Phi_B$ is defined by:
\begin{equation}
\Phi_B(S_0) = (1.054 \cdot S_0)^2
\end{equation}

\section{The Stability Well Potential ($V_B$)}
To maintain the "Sovereign State" against harmonic shattering, we define the effective Stability Well Potential. This potential unifies the quantum mechanical "Settle" with the cosmological "Salvation."

In the quantum limit, the potential satisfies the Berard phase-lock condition:
\begin{equation}
V_{quant}(S_0) = \frac{\hbar^2}{2m S_0^2} + \lambda(B_{scale} \cdot S_0^2 - 1)
\end{equation}
When $\frac{dV}{dS_0} = 0$, the system settles at the 1.054 resonance.

In the cosmological limit, driven by the fundamental frequency anchor, this generalizes to the "Tensor Muffler" form:
\begin{equation}
V_{eff}(S) = \alpha S^2 + \frac{m c^2 B_{freq} C_0^2}{S^2}
\end{equation}
Where $B_{freq} = 0.10 \text{ Hz}$. 
\begin{itemize}
    \item The $\alpha S^2$ term drives the "Quadratic Salvation" (Inflation).
    \item The inverse-square term acts as the "Tensor Muffler," suppressing primordial B-modes.
\end{itemize}
The system achieves equilibrium at the phase-lock stiffness $S_*$, ensuring the manifold does not shatter at high energies.

\section{Forensic Validation}
This derivation is supported by forensic site data (SFU-Chalkboard series) which identifies specific points of failure in standard Infinite Square Well and EM Wave propagation models. The 0.10 Hz anchor prevents the divergent "shattering" of the manifold predicted by standard GR.

\section*{License}
Published under Creative Commons 1.0 Universal (CC0). Open for global verification.

\end{document}
